\pkg{sparseHessianFD}: An R Package for Estimating Sparse Hessian Matrices

### 2016-12-24 nobuild/jss_revision/response.tex

\begin{document}

{\bfseries
\begin{center}
  Manuscript JSS2717\\
 ``sparseHessianFD: An R Package for Estimating Sparse
 Hessian Matrices''\\
 \vspace{\baselineskip}
 Response to reviewer
\end{center}
}
\vspace{\baselineskip}

I would like to express my sincere appreciation for the time and effort that
you invested in the review.  It is obvious to me that you went through
the paper and code in great detail.  In
particular, thank you for bringing the complex step
method to my attention.  I \emph{never} use complex numbers or
functions in my own work, so I typically ignore anything with the word
``complex'' in it.  But this review prompted me to learn something
new, and that is always fun.

I am happy to write that I was able to incorporate a large majority of
your suggestions into the the revised paper and package. For the
others, I hope that you, and the editor, will accept my
explanations and excuses.  Of course, if there are any strong
objections to how I responded to any of the comments, I am happy
to make further changes in advance of publication.

@@

\vspace{\baselineskip}

\begin{enumerate}[align=left]
 \setcounter{enumi}{-1}

\item \begin{revQuote}
I had a minor problem checking the package tarball:

{\normalfont (error messages related to algorithm.sty removed).}

@@

I don't remember if there is an easy way to distribute ``special'' sty files,
or if you must force the user to install them. If the sty is not really
critical it might be better to omit it.

\end{revQuote}

\begin{response}
Because \pkg{sparseHessianFD} passed CRAN check, I suspect that the
error is a result of the \pkg{algorithm} package
not being present in your LaTeX installation.  It is a standard
package in the MacTeX distribution, but I cannot speak with authority about other
platforms. It should be easily installed through CTAN.

### 2016-12-24 nobuild/jss_revision/sparseHessianFD.Rnw
Revert "just about done with revision"
This reverts commit 7bf2fa8d9479891736b9f3fe6828763c350a30bd.

{\setlength{\extrarowheight}{.25em}
\begin{table}[ptb]
\begin{tabularx}{\linewidth}{>{\bfseries}r X}
  \toprule
x& A numeric vector, with length $M$ at which the object will be
  initialized and tested.\\
fn,gr& \proglang{R} Functions that return the value of the
  objective function, and its gradient. The first argument is the numeric
  variable vector.  Other named arguments can be passed to \func{fn}
  and {gr} as well (see the \funcarg{...} argument below).\\
rows, cols& Sparsity pattern: integer vectors of the row and column indices of
  the non-zero elements in the \emph{lower triangle} of the Hessian.\\
delta& The perturbation amount for finite differencing of the
  gradient to compute the Hessian (the $\delta$ in Section~\ref{sec:numdiff}).  Defaults to
  \code{sqrt(.Machine\$double.eps)}.\\
index1& If \variable{TRUE} (the default), \funcarg{row} and \funcarg{col} use one-based
  indexing.  If \variable{FALSE}, zero-based indexing is used.\\
  complex&If \variable{TRUE}, the complex step method is used.
                If \variable{FALSE} (the default), a simple finite
                differencing of gradients is used.\\
...& Additional arguments to be passed to \func{fn} and \func{gr}.\\
 \bottomrule
\end{tabularx}
\caption{Arguments to the sparseHessianFD initializer.}\label{tab:init}
\end{table}
}

>>>>

{\setlength{\extrarowheight}{.25em}
\begin{table}[ptb]
\begin{tabularx}{\linewidth}{>{\bfseries}r X}
  \toprule
x& A numeric vector, with length $M$ at which the object will be
  initialized and tested.\\
fn,gr& \proglang{R} Functions that return the value of the
  objective function, and its gradient. The first argument is the numeric
  variable vector.  Other named arguments can be passed to \func{fn}
  and {gr} as well (see the \funcarg{...} argument below).\\
rows, cols& Sparsity pattern: integer vectors of the row and column indices of
  the non-zero elements in the \emph{lower triangle} of the Hessian.\\
direct& This argument is deprecated, and is included only for
  backwards compatibility with earlier versions.\\
delta& The perturbation amount for finite differencing of the
  gradient to compute the Hessian (the $\delta$ in Section~\ref{sec:numdiff}).  Defaults to
  \code{sqrt(.Machine\$double.eps)}.\\
index1& If \variable{TRUE} (the default), \funcarg{row} and \funcarg{col} use one-based
  indexing.  If \variable{FALSE}, zero-based indexing is used.\\
  complex&If \variable{TRUE}, the complex step method is used.
                If \variable{FALSE} (the default), a simple finite
                differencing of gradients is used.\\
...& Additional arguments to be passed to \func{fn} and \func{gr}.\\
 \bottomrule
\end{tabularx}
\caption{Arguments to the sparseHessianFD initializer.}\label{tab:init}
\end{table}
}
